---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

header-includes:
  - \usepackage[ngerman]{babel}

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r import data, include=FALSE}
library(tidyverse)
library(ggpubr)
block2_results <- readRDS("data/block2_results.rds")
```




# Methoden
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Teilnehmende

## Prozedur

## Datenanalyse
We used <!---`r cite_r("r-references.bib")`---> for all our analyses.


# Ergebnisse

```{r extract q01 values, include=FALSE}
n_qrps <- block2_results$data$q01 %>% 
  summarise(n_qrps = mean(n_qrps_per_proj)) %>% 
  pull(n_qrps) %>% 
  round(2)

sd_qrps <- block2_results$data$q01 %>% 
  summarise(sd_qrps = sd(n_qrps_per_proj)) %>% 
  pull(sd_qrps) %>% 
  round(2)
```

```{r extract q02 values, include=FALSE}
q02 <- block2_results$data$q02

n_qrps_emp.intern <- q02 %>% 
  filter(project == "emp.intern", type_of_practice == "Questionable") %>% 
  pull(practices_per_proj) %>% 
  round(2)

n_qrps_thesis.msc <- q02 %>% 
  filter(project == "thesis.msc", type_of_practice == "Questionable") %>% 
  pull(practices_per_proj) %>% 
  round(2)
```

```{r extract q03 and q05 values, include=FALSE}
q03 <- block2_results$data$q03
q05 <- block2_results$data$q05

share_no_sample_planning <- q05 %>% 
  filter(practice == "No Sample Planning") %>% 
  pull(share) %>% 
  round(2)

share_sr_of_variables <- q05 %>% 
  filter(practice == "SR of Variables") %>% 
  pull(share) %>% 
  round(2)

share_rounding_p_values <- q05 %>% 
  filter(practice == "Rounding p-Values") %>% 
  pull(share) %>% 
  round(2)

share_flexible_sample_size <- q05 %>% 
  filter(practice == "Flexible Sample Size") %>% 
  pull(share) %>% 
  round(2)
```

Aus den Angaben der Teilnehmenden ergab sich ein mittlerer Einsatz von `r n_qrps` fragwürdigen Forschungspraktiken (SD = `r sd_qrps`) pro Projekt. Wie in \autoref{fig:plot02} zu sehen ist, zeigten sich dabei Unterschiede zwischen den abgefragten Projekten. Besonders viele fragwürdige Praktiken scheinen demnach mit durchschnittlich `r n_qrps_emp.intern` Praktiken pro Projekt im Expra verwendet zu werden, während Masterarbeiten mit durchschnittlich `r n_qrps_thesis.msc` verwendeten fragwürdigen Praktiken den niedrigsten Wert aufweisen. 

```{r plot02, fig.cap="\textbf{Anzahl eingesetzter fragwürdiger Forschungspraktiken pro Projekt.} Schwarze Punkte stellen den Mittelwert dar. Die Anzahl ist ganzzahlig, die Punkte wurden mit zufälliger Streuung versehen."}
block2_results$plots$plot02 + labs(title = NULL, subtitle = NULL,
                                   ylab = "Anzahl eingesetzter QRPs", 
                                   xlab = "Projekt")
```

In \autoref{fig:plot0305} ist die Einsatzhäufigkeit der einzelnen abgefragten Forschungspraktiken dargestellt. Als am häufigsten eingesetzte fragwürdige Forschungsmethoden zeigten sich fehlende Stichprobenplanung und selektives Berichten abhängiger Variablen (`r share_no_sample_planning`, bzw. `r share_sr_of_variables` % der Projekte betroffen). Die von unseren Teilnehmenden am seltensten eingesetzten Methoden waren das Abrunden von p-Werten und das Nacherheben von Versuchspersonen zum Zweck der Herbeiführung statistischer Signifikanz (`r share_rounding_p_values`, bzw. `r share_flexible_sample_size` % der Projekte betroffen).


```{r plot0305, fig.cap="Caption"}
plot03 <- block2_results$plots$plot03 + 
  #labs(title = NULL, subtitle = NULL) +
  NULL

plot05 <- block2_results$plots$plot05 + 
  labs(title = NULL, subtitle = NULL) +
  NULL

plot05

#ggpubr::ggarrange(plot03, plot05, ncol = 1, nrow = 2)
```


# Diskussion


\newpage

# References
```{r create_r-references}
# r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
