---
title: "Descriptives"
subtitle: "PsyFaKo Open Science Survey"
author: "Johannes Brachem"
date: "Last update: `r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    number_sections: yes
    theme: journal
    toc: yes
    toc_depth: 2
    toc_float: 
      collapsed: false
---

# Header

## Load Packages
```{r packages}
library(tidyverse)
library(skimr)
library(formr)
```

## Session Info
```{r session info}
sessionInfo()
```

## Import Data

```{r import data}
main <- read_csv("data/main.csv")

n_obs_uni <- read_csv("data/n_observations_uni.csv")
```

# All Psychology Students

```{r}
main_descriptives_full<- main %>% 
  filter(field_of_study_mc == "Psychology" | study_degree_field == "Psychology") %>% 
  select(age, sex, semester, study_stage_mc, study_stage_open, 
         uni_bachelor, uni_current, study_degree, study_degree_field, 
         study_degree_year, study_degree_yesno, comments, exp_specific)


# Number of included participants.
(n_participants_full <- main_descriptives_full %>% nrow())

# General overview
main_descriptives_full %>% skim()

# Participants' genders
main_descriptives_full %>% pull(sex) %>% table()

# Percentages of participants' genders
(main_descriptives_full %>% pull(sex) %>% table()) / n_participants_full * 100

# Look at age distribution
main_descriptives_full %>% pull(age) %>% hist(main = "Age Histogram", xlab="age")
main_descriptives_full %>% pull(age) %>% table()

# Raw number of participants per semester and study stage
main_descriptives_full %>% 
  filter(study_stage_mc != "Other") %>% 
  filter(semester < 11) %>% 
  mutate(semester = ifelse(semester %% 2 == 0, semester - 1, semester)) %>% 
  mutate(semester = factor(semester, 
                           labels = c("1/2", "3/4", "5/6", "7/8", "9/10"))) %>% 
  group_by(semester, study_stage_mc) %>% 
  summarise(n = n()) %>% 
  arrange(study_stage_mc)

# Percentages of participants in different study stages
(main_descriptives_full %>% pull(study_stage_mc) %>% 
    table()) / n_participants_full *100
```

# Participants with empirical experience
Sample description for the participants who indicated that they have so far conducted at least one empirical project in the course of their studies.

```{r}
main_descriptives_filtered <- main %>% 
  filter(field_of_study_mc == "Psychology" | study_degree_field == "Psychology") %>% 
  filter(emp_experience == "Yes") %>% 
  select(age, sex, semester, study_stage_mc, study_stage_open, 
         uni_bachelor, uni_current, study_degree, study_degree_field, 
         study_degree_year, study_degree_yesno, comments, exp_specific)

# Number of included participants.
(n_participants <- main_descriptives_filtered %>% nrow())

# General overview
main_descriptives_filtered %>% skim()

# Participants' genders
main_descriptives_filtered %>% pull(sex) %>% table()

# Percentages of participants' genders
(main_descriptives_filtered %>% pull(sex) %>% table()) / n_participants * 100

# Look at age distribution
main_descriptives_filtered %>% pull(age) %>% hist(main = "Age Histogram", xlab="age")
main_descriptives_filtered %>% pull(age) %>% table()

# Percentages of participants in different study stages
(main_descriptives_filtered %>% pull(study_stage_mc) %>% table()) / n_participants *100

# Raw number of participants per semester and study stage
main_descriptives_filtered %>% 
  filter(study_stage_mc %in% c("Bachelor", "Master")) %>% 
  mutate(semester = ifelse(semester %% 2 == 0, semester - 1, semester)) %>% 
  mutate(semester = ifelse(semester > 10, 11, semester)) %>% 
  mutate(semester = factor(semester, 
                           labels = c("1/2", "3/4", "5/6", "7/8", "9/10", ">10"))) %>% 
  group_by(semester, study_stage_mc) %>% 
  summarise(n = n()) %>% 
  arrange(study_stage_mc)

# Number of Projects
main_descriptives_filtered$exp_specific %contains% "1" %>% sum() # Expra
main_descriptives_filtered$exp_specific %contains% "2" %>% sum() # Project
main_descriptives_filtered$exp_specific %contains% "3" %>% sum() # Bachelor's Thesis
main_descriptives_filtered$exp_specific %contains% "4" %>% sum() # Master's Thesis
main_descriptives_filtered$exp_specific %contains% "5" %>% sum() # Other
```

## Data points per university (emp experience subset)
These numbers concern only the subset of participants who indicated that they have conducted at least one empirical project in the course of their studies. We count psychology students and former psychology students who graduated 2017 or later. Subjects who studied at two different universities for their bachelor's and master's degree are counted as a data point for each of the universities.

```{r}
# Data points per university
n_obs_uni %>% arrange(desc(n)) %>% print(n = nrow(.))

# Total number of data points
n_obs_uni %>% pull(n) %>% sum()
```